Comparison of approaches to using machine learning models to increase the efficiency of the global search algorithm for solving multicriterial problems

### 2024-06-29 2024/OPTIMA/OPTIMA_2024_MCO.tex
OPTIMA add 4c alpha=0

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage{graphicx}
\begin{table}[ht]
\centering
\caption{Results of computational experiments}
\label{tab:1}
\resizebox{\textwidth}{!}{%
\begin{tabular}{cccccc}
\hline
\textbf{}                                                                                  & \textbf{Model Kernel} & \textbf{$\alpha$} & \textbf{Avg. HV-index} & \textbf{Avg. iter.} & \textbf{Speedup iter.} \\ \hline
ML\_MGSA                                                                                   & -                     & -                              & 114.91                 & 2269.82             & 1.00                   \\ \hline
\multicolumn{6}{c}{\textbf{Experiments for the case of fixed weights}}                                                                                                                                                      \\ \hline
ML\_MGSA\_Dist                                                                             & Linear                & 0.01                           & 114.67                 & 691.14              & \textbf{3.28}          \\
\multirow{3}{*}{ML\_MGSA\_Prob (Fixed weights)} & Linear                & 0.04                           & 114.72                 & 963.05              & 2.36                   \\
                                                                                           & Poly                  & 0.07                           & 114.73                 & 871.82              & 2.60                   \\
                                                                                           & RBF                   & 0.03                           & 114.80                 & 883.04              & 2.57                   \\ \hline
\multicolumn{6}{c}{\textbf{Experiments for the case of adjusted weights}}                                                                                                                                                   \\ \hline
ML\_MGSA\_Dist                                                                             & Linear                & 0.01                           & 114.67                 & 691.14              & \textbf{3.28}          \\
\multirow{3}{*}{ML\_MGSA\_Prob (Adj. weights)}  & Linear                & 0.04                           & 114.76                 & 1018.03             & 2.23                   \\
                                                                                           & Poly                  & 0.08                           & 114.73                 & 844.66              & 2.69                   \\
                                                                                           & RBF                   & 0.03                           & 114.76                 & 796.74              & 2.85                   \\ \hline
\multicolumn{6}{c}{\textbf{Experiments for the case of adjusted weights and logarithmic probabilities}}                                                                                                                              \\ \hline
ML\_MGSA\_Dist                                                                             & Linear                & 0.01                           & 114.67                 & 691.14              & \textbf{3.28}          \\
\multirow{3}{*}{ML\_MGSA\_Prob (Log Norm)}      & Linear                & 0.05                           & 114.72                 & 711.44              & 3.19                   \\
                                                                                           & Poly                  & 0.04                           & 114.79                 & 854.82              & 2.66                   \\
                                                                                           & RBF                   & 0.04                           & 114.74                 & 704.99              & 3.22                   \\ \hline
\multicolumn{6}{c}{\textbf{Experiments with 4-criterial MCO problems}}                                                                                                                                                      \\ \hline
ML\_MGSA\_Dist                                                                             & Linear                & 0.01                           & 7751.43                & 1925.6              & 1.00                   \\
\multirow{3}{*}{ML\_MGSA\_Prob (Log Norm)}      & Linear                & 0.08                           & 7729.71                & 1760.5              & 1.09                   \\
                                                                                           & Poly                  & 0.08                           & 7796.2                 & 4121.7              & 0.47                   \\
                                                                                           & RBF                   & 0.08                           & 7786.48                & 1364.6              & \textbf{1.41}          \\ \hline
\end{tabular}%
}
\end{table}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage{graphicx}
\begin{table}[ht]
\centering
\caption{Results of computational experiments}
\label{tab:1}
\resizebox{\textwidth}{!}{%
\begin{tabular}{cccccc}
\hline
\textbf{}                                                                  & \textbf{Model Kernel} & \textbf{$\alpha$} & \textbf{Avg. HV-index} & \textbf{Avg. iter.} & \textbf{Speedup iter.} \\ \hline
ML\_MGSA                                                                   & -          & -    & 114.91  & 2269.82   & 1.00           \\ \hline
\multicolumn{6}{c}{\textbf{Experiments for the case of fixed weights}}                                                                \\ \hline
ML\_MGSA\_Dist                                                             & Linear     & 0.01 & 114.67  & 691.14    & \textbf{3.28}  \\
\multirow{3}{*}{ML\_MGSA\_Prob (Fixed weights)}                            & Linear     & 0.04 & 114.72  & 963.05    & 2.36           \\
                                                                           & Poly       & 0.07 & 114.73  & 871.82    & 2.60           \\
                                                                           & RBF        & 0.03 & 114.80  & 883.04    & 2.57           \\ \hline
\multicolumn{6}{c}{\textbf{Experiments for the case of adjusted weights}}                                                             \\ \hline
ML\_MGSA\_Dist                                                             & Linear     & 0.01 & 114.67  & 691.14    & \textbf{3.28}  \\
\multirow{3}{*}{ML\_MGSA\_Prob (Adj. weights)}                             & Linear     & 0.04 & 114.76  & 1018.03    & 2.23           \\
                                                                           & Poly       & 0.08 & 114.73  & 844.66    & 2.69           \\
                                                                           & RBF        & 0.03 & 114.76  & 796.74    & 2.85           \\ \hline
\multicolumn{6}{c}{\textbf{Experiments for the case of adjusted weights and logarithmic probabilities}}                                               \\ \hline
ML\_MGSA\_Dist                                                             & Linear     & 0.01 & 114.67  & 691.14    & \textbf{3.28}  \\
\multirow{3}{*}{ML\_MGSA\_Prob (Log Norm)}                                 & Linear     & 0.05 & 114.72  & 711.44    & 3.19           \\
                                                                           & Poly       & 0.04 & 114.79  & 854.82    & 2.66           \\
                                                                           & RBF        & 0.04 & 114.74  & 704.99    & 3.22           \\ \hline
\multicolumn{6}{c}{\textbf{Experiments with 4-criterial MCO problems}}                                                                \\ \hline
ML\_MGSA                                                                   & -          & -    & 7819.86 & 6046.4    & 1.00           \\ \hline
ML\_MGSA\_Dist                                                             & Linear     & 0.01 & 7751.43 & 1925.6    & 3.14           \\
\multirow{3}{*}{ML\_MGSA\_Prob (Log Norm)}                                 & Linear     & 0.08 & 7729.71 & 1760.5    & 3.43           \\
                                                                           & Poly       & 0.08 & 7796.20 & 4121.7    & 1.47           \\
                                                                           & RBF        & 0.08 & 7786.48 & 1364.6    & \textbf{4.43}  \\ \hline
\end{tabular}%
}
\end{table}
